### 2021-06-23 chapters/3_background.tex
redo structure

\section{Clustering algorithms}
This research focuses on clustering mutants and use of existing clustering algorithms. 
Many different types of clustering algorithms have been proposed\cite{Rodriguez2019}. While there is a lot of diversity, some methods are more frequently used than others\cite{Wu2008TopMining}. 
Rodriguez et al., compared the performance of nine different clustering algorithms:
\begin{itemize}
    \item k-means
    \item CLARA
    \item hierarchical
    \item EM
    \item hcmodel
    \item spectral
    \item subscpace
    \item optics
    \item dbscan
\end{itemize}
The goal of their study was to guide researchers, who have little experience in data mining techniques, to the application of clustering methods.
They evaluated the algorithms in three distinct situations: default parameters, single parameter variation and random variation of parameters.
They used 400 generated artificial data sets which were normally distributed.
\newline
The results reported in their research are respective to specific configurations of normally distributed data and algorithmic implementations.
Nonetheless they do give a good overview on how the algorithms compare to each other.
\newline
For the default parameter situation the spectral clustering algorithm had the best performance and the hierarchical algorithm had the worst performance.
\newline
Regarding single parameter variations, for data sets containing 2 columns, the hierarchical, optics and EM methods showed significant performance variation.
\newline
With respect to the multidimensional analysis for data sets, the performance of the algorithms for the multidimensional selection of parameters was similar to that using the default parameters.
They conclude their research with observing that, for data sets with 10 or more columns the spectral algorithm consistently provided the best performance.
However the EM, hierarchical, k- means and subspace algorithms can also achieve similar performance with some parameter tuning.
The optics and dbscan algorithms aim at different data distributions than performed in this study. There different results could be obtained for non-normally distributed data.
\end{document}

>>>>

\section{Clustering algorithms}
This research focuses on clustering mutants and use of existing clustering algorithms. 
Many different types of clustering algorithms have been proposed\cite{Rodriguez2019}. While there is a lot of diversity, some methods are more frequently used than others\cite{Wu2008TopMining}. 
Rodriguez et al., compared the performance of nine different clustering algorithms:
\begin{itemize}
    \item k-means
    \item CLARA
    \item hierarchical
    \item EM
    \item hcmodel
    \item spectral
    \item subscpace
    \item optics
    \item dbscan
\end{itemize}
The goal of their study was to guide researchers, who have little experience in data mining techniques, to the application of clustering methods.
They evaluated the algorithms in three distinct situations: default parameters, single parameter variation and random variation of parameters.
They used 400 generated artificial data sets which were normally distributed.
\newline
The results reported in their research are respective to specific configurations of normally distributed data and algorithmic implementations.
Nonetheless they do give a good overview on how the algorithms compare to each other.
\newline
For the default parameter situation the spectral clustering algorithm had the best performance and the hierarchical algorithm had the worst performance.
\newline
Regarding single parameter variations, for data sets containing 2 columns, the hierarchical, optics and EM methods showed significant performance variation.
\newline
With respect to the multidimensional analysis for data sets, the performance of the algorithms for the multidimensional selection of parameters was similar to that using the default parameters.
They conclude their research with observing that, for data sets with 10 or more columns the spectral algorithm consistently provided the best performance.
However the EM, hierarchical, k- means and subspace algorithms can also achieve similar performance with some parameter tuning.
The optics and dbscan algorithms aim at different data distributions than performed in this study. There different results could be obtained for non-normally distributed data.

\section{Neural networks for clustering}
There are many different types of neural networks.
These neural networks have different applications based on their properties.
For this thesis we will focus on neural networks designed for clustering.
\newline
Neural networks consists of machine learning algorithms\cite{supervisedUnsupervised}. 
These machine learning algorithms are divided in supervised and unsupervised learning algorithms\cite{supervisedUnsupervised}.
Supervised machine learning algorithms are commonly used for classification and categorization\cite{supervisedUnsupervised}.
Unsupervised machine learning algorithms are commonly used for clustering and dimensionality reduction\cite{supervisedUnsupervised}.
\newline
K.L. Du surveyed different neural networks and algorithms used for clustering:
\begin{itemize}
    \item Self organizing map.
    \item Learning vector quantization.
    \item C-means clustering.
    \item Mountain and Substractive clustering.
    \item Neural gas.
    \item ART networks.
    \item Fuzzy c-means.
\end{itemize}
In his paper he also touches on subjects relevant to clustering and neural networks such as the under-utilization problem, fuzzy clustering, robust clustering, clustering based on non- Euclidean distance measures, supervised clustering, and hierarchical clustering.
Neural network variants and their references are also discussed.
\newline
K.L. Du describes the mathematical principles on which the neural networks and algorithms are based.
He closes his paper with computer simulations of some of the neural networks he surveyed.

\end{document}

### 2021-06-23 chapters/rq1/2_experiment_design.tex
redo structure

\subsection{Validation}
The most efficient way to measure test effectiveness with mutation testing is by running all mutants that a tool can possibly generate.
The goal of this experiment is to reduce the amount of mutants executed while maintaining effectiveness.
To reduce the amounts executed we cluster the mutants. 
We can measure this by counting the amount of clusters we generate and compare it to the number of total mutants generated by the selected tool.
\newline
The baseline for our experiment is the mutation score of the set of all mutants generated by our selected mutation testing tool.
\newline
To validate how effective our clustering is we can compare the weighed mutation score(see Chapter \ref{ch:weighed_score}) of our clustered set to the mutation score of the full set.
The closer the weighed score is to that of a full set the more effective our set of characteristics and clustering algorithm proves to be.
In other words we want achieve a mutation score that is as close as possible as to that of a full set.
We select a significance level of $\leq 0.05$.
This is the conventional threshold for declaring statistical significance\cite{Kirk1996PracticalCome}.
\newline
Depending on the effectiveness of our clustering algorithm we may loose accuracy.
This can happen if a cluster contains mutants both types. 
We can measure this accuracy by calculating a percentage of all mutants that have survived against the ones that have been killed in a cluster.
If the majority of the mutants in a cluster is killed then we consider that cluster to represent a killed cluster and the other way around for survived mutants.
We consider the mutants that are not in the majority of the cluster as inaccuracy.
\newline
To decide if we accept or reject our hypothesis we use statistical significance\cite{Kirk1996PracticalCome}.
If the weighed mutation score of our clustered set deviates more than 5\% from the score of a full set we will reject our hypothesis.
We also compare the inaccuracy to the significance level to decide if our inaccuracy is statistical significant.
\end{document}

>>>>

\subsection{Validation}
The most efficient way to measure test effectiveness with mutation testing is by running all mutants that a tool can possibly generate.
The goal of this experiment is to reduce the amount of mutants executed while maintaining effectiveness.
To reduce the amounts executed we cluster the mutants. 
We can measure this by counting the amount of clusters we generate and compare it to the number of total mutants generated by the selected tool.
\newline
The baseline for our experiment is the mutation score of the set of all mutants generated by our selected mutation testing tool.
\newline
To validate how effective our clustering is we can compare the weighed mutation score(see Chapter \ref{ch:weighed_score}) of our clustered set to the mutation score of the full set.
The closer the weighed score is to that of a full set the more effective our set of characteristics and clustering algorithm proves to be.
In other words we want achieve a mutation score that is as close as possible as to that of a full set.
We select a significance level of $\leq 0.05$.
This is the conventional threshold for declaring statistical significance\cite{Kirk1996PracticalCome}.
\newline
Depending on the effectiveness of our clustering algorithm we may loose accuracy.
This can happen if a cluster contains mutants both types. 
We can measure this accuracy by calculating a percentage of all mutants that have survived against the ones that have been killed in a cluster.
If the majority of the mutants in a cluster is killed then we consider that cluster to represent a killed cluster and the other way around for survived mutants.
We consider the mutants that are not in the majority of the cluster as inaccuracy.
\newline
To decide if we accept or reject our hypothesis we use statistical significance\cite{Kirk1996PracticalCome}.
If the weighed mutation score of our clustered set deviates more than 5\% from the score of a full set we will reject our hypothesis.
We also compare the inaccuracy to the significance level to decide if our inaccuracy is statistical significant.

\subsection{Mutant selection}
As stated in our hypothesis we will randomly select a mutant from each cluster to be executed.
To make our results reproducible we will select a random mutant based on a generated seed.
The seed generated for each run will be included in the results and can be found in the Github repository\cite{rbasarat-repo}.
Achieving consistent results while applying random selection will contribute to the validity of the experiment.
We will use the same statistical significance threshold to decide if the variation by the random sampling is acceptable or not.

\end{document}
